Navigating Hostility: The Effect of Nonprofit Transparency and Accountability on Donor Preferences in the Face of Shrinking Civic Space

### 2025-01-22 README.qmd
Update Zenodo DOI

<!-- badges: start -->
[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fhu6a5-blue)](https://doi.org/10.31235/osf.io/hu6a5) [![OSF DOI](https://img.shields.io/badge/OSF%20project-10.17605%2FOSF.IO%2FR59XZ-blue)](https://doi.org/10.17605/OSF.IO/R59XZ) [![Code DOI](https://img.shields.io/badge/Code-10.5281%2Fzenodo.14220206-blue)](https://doi.org/10.5281/zenodo.14220206)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Preprint](https://img.shields.io/badge/Preprint-10.31235%2Fosf.io%2Fhu6a5-blue)](https://doi.org/10.31235/osf.io/hu6a5) [![OSF DOI](https://img.shields.io/badge/OSF%20project-10.17605%2FOSF.IO%2FR59XZ-blue)](https://doi.org/10.17605/OSF.IO/R59XZ) [![Code DOI](https://img.shields.io/badge/Code-10.5281%2Fzenodo.14721277-blue)](https://doi.org/10.5281/zenodo.14721277)
<!-- badges: end -->
